\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-10 paper/main.tex
.

We spent a significant amount of time testing different evaluation
schemes for predicting drug--target interactions. We designed a
na\"ive predictor and find that it can achieve a performance only
slightly below state of the art drug--target prediction methods. We
investigated this finding further and

@@

\todo[inline]{Likely discussion:} The most common scheme for DTI
prediction is the split over drug-target pairs \citep{Survey2018},
where likely all drugs and targets of the validation and testing phase
have already occurred in the training phase, as part of other
drug-target pairs. The second most prevalent arrangement is the split
over drugs, while only close to none is aiming on a protein split.
However, the first and second splitting scheme are exposed to the
first dataset bias and are hence more likely vulnerable to
transductive inference by just predicting recently seen structures,
rather than implementing inductive inference and generalizing over the
drug representations. Second, these two strategies are more
susceptible to the second bias, as only in these cases the model may
overfit on the number of existing interactions for a single protein,
while in the third scheme the number of interactions of the test
proteins is entirely unknown during training process.

>>>>

One major component of our experiments was to determine how the
information that is available to a machine learning model during
training affects the performance of the model. Similarly to previous
work, we find significant differences in predictive performance across
different splitting schemes.

The most common scheme for drug--target interaction prediction is the
split over drug-target pairs \cite{Survey2018} where it may happen
that most drugs and targets that are including in the model's
validation and testing phase have also been included in the training
phase (as part of other drug--target pairs).

The second most prevalent arrangement is the split
over drugs, while only close to none is aiming on a protein split.
However, the first and second splitting scheme are exposed to the
first dataset bias and are hence more likely vulnerable to
transductive inference by just predicting recently seen structures,
rather than implementing inductive inference and generalizing over the
drug representations. Second, these two strategies are more
susceptible to the second bias, as only in these cases the model may
overfit on the number of existing interactions for a single protein,
while in the third scheme the number of interactions of the test
proteins is entirely unknown during training process.

We designed a
na\"ive predictor and find that it can achieve a performance only
slightly below state of the art drug--target prediction methods. We
investigated this finding further and

@@
